---
title: "Simulation 2"
author: "Jeremy J Lin"
date: "`r Sys.Date()`"
output: 
  pdf_document :
    keep_tex: true
    extra_dependencies: "subfig"
header-includes:
 - \usepackage{booktabs}
 - \usepackage{longtable}
 - \usepackage{array}
 - \usepackage{multirow}
 - \usepackage{wrapfig}
 - \usepackage{float}
 - \usepackage{subfig}
 - \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nlme)
library(Matrix)
library(MASS)
library(rootSolve)
library(geepack)
library(lme4)
library(mvtnorm)
library(reshape2)
library(knitr)
library(ggplot2)
library(tidyr)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(kableExtra)
library(corrplot)
library(robustHD)
library(pracma)
library(xtable)
library(latex2exp)
library(janitor)
library(ggpubr)
# parallel computing libraries
library(foreach)
#library(doMC)
# beep beep 
library(beepr)
library(doParallel)
library(doSNOW)
library(utils)
library(foreach)
library(doRNG)
library(geepack)
```

```{r echo=FALSE}
#rm(list = ls())

knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, results = "hide", 
                      fig.pos = 'H', cache = FALSE, 
                      eval = FALSE)
# load functions
source("~/Research/LMM_Project/dgm simutlations/R_functions.R")
```

<!-- Functions -->

# Simulation Settings 

Repeated across 400 simulations with different combination of small total T and small total n.
We would like to compare this with the theoretical asymptotic variance with sample size adjustment

Availability depends on time, with linear treatment effect 

\begin{align*}
  Y_{i, t, 1} | H_t, A_t &= I_{(A_{i,t} = 1)} \beta_1 + I_{(A_{i,t} = 2)} \beta_2 + 1 + \epsilon_{i,t}\\
  A_{i,t} &= \{0, 1, 2\}\\
  P(A_t = 0 |H_t) &=\tilde{p_0}  = 0.2\\
  P(A_t = 1 |H_t) &=\tilde{p_1}  = 0.5\\
  P(A_t = 2 |H_t) &=\tilde{p_2}  = 0.3\\
  P(I_t = 0.5)\\
  \beta_1 &= 0.1\\
  \beta_2 &= 0.4
\end{align*}

```{r}
# change font size, legend position
myggfont <- function(legend_pos = NULL,
                     legend_text_size = 18,
                     legend_title_size = 20,
                     axis_text_size = 22,
                     axis_title_size = 26,
                     plot_title_size = 20,
                     facet_text_size = 16) {
  ff <- theme(legend.text = element_text(size = legend_text_size),
              legend.title = element_text(size = legend_title_size),
              axis.text = element_text(size = axis_text_size),
              axis.title = element_text(size = axis_title_size, face="bold"),
              plot.title = element_text(size = plot_title_size),
              strip.text.x = element_text(size = facet_text_size),
              strip.text.y = element_text(size = facet_text_size))
  if (is.null(legend_pos)) {
    return(ff)
  } else if (legend_pos == "top-left") {
    return(ff + theme(legend.justification = c(0,1), legend.position = c(0,1)))
  } else if (legend_pos == "top-right") {
    return(ff + theme(legend.justification = c(1,1), legend.position = c(1,1)))
  } else if (legend_pos == "bottom-left") {
    return(ff + theme(legend.justification = c(0,0), legend.position = c(0,0)))
  } else if (legend_pos == "bottom-right") {
    return(ff + theme(legend.justification = c(1,0), legend.position = c(1,0)))
  } else {
    stop("legend_pos needs to be NULL, top-left, top-right, bottom-left, or bottom-right.")
  }
}
```


```{r}
n_seed = 63

SD = data.frame()
for (isim in 1:n_seed) {
  fileName = paste("results_sim_1_setting_",isim,"_",1000,".RDS",sep = "")
  res <- readRDS(paste0(fileName))
  print(length(res))
  SD <- rbind(SD, res)
}

saveRDS(SD, "n_vs_AA.RDS")


```


```{r}
# 1. Make plots for n versus ATE------------------------------------------------
    n_ATE <- readRDS("n_vs_AA.RDS")
    
    n_ATE <- n_ATE[which(!is.na(n_ATE$n)),]
    
    n_ATE %>%
    filter(ASPNC_t == 0.08) %>% 
    ggplot(aes(x = AvgTau_w, y = n)) +
    geom_line() +
    # scale_color_discrete(name = "EO(t)",
    #                          labels = c(TeX(r'(constant)'),
    #                                     TeX(r'(linear)'),
    #                                     TeX(r'(quadratic)')))+
    xlab(TeX(r'(AA)')) +
    ylab("n (sample size)") +
    # ggtitle("constant MEE(t) and SPNC(t)") +
    #coord_cartesian(ylim = c(5000, 9000), xlim = c(1.3, 1.6)) +
    #scale_x_continuous(breaks = c(1.05, 1.1, 1.2, 1.3, 1.4)) +
    theme_bw() + 
    myggfont() +
    theme(legend.text.align = 0, plot.title = element_text(hjust = 0.5))
ggsave("Drinkless 1 - n vs AA.jpg", height = 6, width = 6)
ggsave("Drinkless 1 - n vs AA.pdf", height = 6, width = 6)

```


```{r}
n_ATE %>% 
  filter(n < 500) %>% 
  ggplot(aes(x = ATE1_t, y = ATE2_t, color = n)) +
  geom_point()


```


```{r}
library(metR)
n_ATE %>%
    #filter(ATE1_t <= 1.09) %>%
    ggplot(aes(x = ATE1_t, y = ATE2_t, z = n, color = factor(ASPNC_t))) +
    geom_contour(binwidth = 1000) +
    geom_text_contour(skip = 0, stroke = 0.2, size = 5) +
    xlab("ATE 1") +
    ylab("ATE 2") +
    # ggtitle("contour: sample size n") +
    theme_bw() + 
    myggfont() +
    theme(legend.text.align = 0, plot.title = element_text(hjust = 0.5))
ggsave("size Drink Less 1 - n vs ASPN, ATE (contour).jpg", height = 6, width = 6)
```



```{r}
n_ATE %>%
    filter(ATE1_t <= 1.15, ATE2_t > 1.2, ASPNC_t %in%c(0.03, 0.08)) %>%
    ggplot(aes(x = ATE1_t, y = ATE2_t, z = n, color = factor(ASPNC_t))) +
    geom_abline(slope = 1, intercept = 0, color = "black", linetype = "dashed") +
    geom_contour(binwidth = 1000) +
    geom_text_contour(skip = 0, stroke = 0.2, size = 5) +
    xlab("ATE 1") +
    ylab("ATE 2") +
    # ggtitle("contour: sample size n") +
    theme_bw() + 
    myggfont() +
    theme(legend.text.align = 0, plot.title = element_text(hjust = 0.5))
ggsave("size Drink Less 1 - n vs ASPN = 0.1, ATE (contour).jpg", height = 6, width = 6)
```


```{r}
# check if sample size is the same for every delta ATE
n_ATE %>% 
filter(n>=2000, n<= 6000)   %>% 
  ggplot(aes(x = ATE1_t, y = ATE2_t, z = n, linetype = factor(ASPNC_t))) +
    #geom_abline(slope = 1, intercept = 0, color = "black", linetype = "dashed") +
    #geom_contour(binwidth = 50) +
    #geom_text_contour() +
    geom_contour_filled() +
    scale_fill_viridis_d(option = "plasma") +  # nice perceptually uniform colormap
    coord_equal() +
    xlab("ATE 1") +
    ylab("ATE 2") +
    # ggtitle("contour: sample size n") +
    theme_bw() + 
    myggfont() +
    theme(legend.text.align = 0, plot.title = element_text(hjust = 0.5))
ggsave("size Drink Less 1 - n vs ASPN = 0.1, ATE (contour).jpg", height = 6, width = 6)
```
